---
title: "Stats analysis for Mat"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
theme: cosmo
---

## Intro

A survey based study into student preferences for a polling tool in revision lessons.

## Questions

Below are the survey questions in the survey.

#### Q1.  "For Revision Class 1 (on Tuesday 6th August), did you:"

1. face-to-face

2. recording

3. livestream

4. did not attend

#### Q2. "If you attended Revision Class 1, did you answer any questions aloud in front of the class?"

1. Yes, 1

2. Yes >1

3. No

#### Q3. "How comfortable did you feel to answer questions in Revision Class 1?"

1. Extremely comfortable

4. Neutral

7. Extremely comfortable

#### Q4. "How would you rate the usefulness of Revision Class 1 for understanding the topics covered?"

1. Extremely useful

2. Very useful

3. Moderately useful

4. Slightly useful 

5. Not useful at all

#### Q5. "How would you rate your overall satisfaction with Revision Class 1?"

1. Extremely satisfied

4. Neutral

7. Extremely satisfied

#### Q6. "Any comments about Revision Class 1 and answering questions aloud during the class?"

Qualitative answer in text box.

#### Q7. "For Revision Class 2 (Monday 26th August, using the Socrative App), did you:"

1. Face-to-face

2. Recording

3. Livestream

4. Did not attend

#### Q8. "If you attended Revision Class 2, did you use the Socrative App to answer any questions?"

1. Yes, 1

2. Yes >1

3. No

#### Q9. "How comfortable did you feel to answer questions in Revision Class 2 using the Socrative App?"

1. Extremely comfortable

4. Neutral

7. Extremely comfortable

#### Q10. "How would you rate the usefulness of Revision Class 2 for understanding the topics covered?"

1. Extremely useful

2. Very useful

3. Moderately useful

4. Slightly useful 

5. Not useful at all

#### Q11. "How would you rate your overall satisfaction with Revision Class 2?"

1. Extremely satisfied

4. Neutral

7. Extremely satisfied

#### Q12. "Any comments about Revision Class 2 and using the Socrative App?"

Qualitative answer in text box.

#### Q13. "Overall, did you prefer Revision Class 1 (traditional method of answering questions aloud during the class), or Revision class 2 (using the Socrative App to answer questions)?"

1. Class 1 with traditional method

2. Class 2 with Socrative

#### Q14. "For future revision classes, which method would you prefer to be used?"

1. Traditional method

2. Socrative method

## Load the data

```{r,read}
x <- read.csv("Revision Class Survey SLE346 T2 2019_September 12, 2019_11.26_for MZ fmt.csv")
head(x)
str(x)

```

## Matt's direction for statistical analysis

For the comparison, I am mainly interested in the responses comparing Class 1 (verbal answers) with Class 2 (Socrative app).

So in my original analyses I am mostly interested in comparing:

### How many questions the students answered in each class (Q2 v Q8)

The first approach to answer will be to use the three levels of participation and test with a Wilcox test and generate the confidence intervals with a t-test.

```{r , participation}
part <- x$Q2
part <- part[which(part!="")]
part <- gsub('Yes \\(more than one question\\)',"2",part)
part <- gsub("No","0",part)
part1 <- as.numeric(part)
# participation for class 1
part1
part <- x$Q8
part <- part[which(part!="")]
part <- gsub('Yes \\(but only a few of the questions\\)',"1",part)
part <- gsub('Yes \\(all or almost all of the questions\\)',"2",part)
part <- gsub("No","0",part)
part2 <- as.numeric(part)
# participation for class 2
part2
par(mfrow=c(2,1), cex=0.8)
hist(part1)
hist(part2)
wilcox.test(part1,part2)
t.test(part1,part2)
```

According to the t-test the participation was higher in class 2.

An alternative approach would be to perform binary classify of students as non-participants or participants and then run a Fisher exact test.

```{r , fisher test}
part1
class1_nonparticipants = length(which(part1==0))
class1_participants = length(which(part1!=0))
class2_nonparticipants = length(which(part2==0))
class2_participants = length(which(part2!=0))
row1 <- c(class1_nonparticipants,class1_participants)
row2 <- c(class2_nonparticipants,class2_participants)
y <- rbind(row1,row2)
rownames(y) <- c("class1","class2")
colnames(y) <- c("non participation","participation")
y
fisher.test(y)

# participation rate class 1 (%)
p1 = my.table[1,2]/sum(my.table[1,])*100
p1

# participation rate class 2 (%)
p2 = my.table[2,2]/sum(my.table[2,]) *100
p2

# increase in participation (%)
p2/p1 * 100
```

Again the p-value is very small indicating a significant difference in participation rates.

### How comfortable they were to answer questions (Q3 v Q9), 

This is a quantitative measure of discomfort so can use Wilcox test or t-test on ranks. Scale: 1 (extremely comf) to 7 (extremely uncomf).

```{r}
# class 1 comfort
x$Q3
comf <- x$Q3
comf <- comf[which(comf!="")]
comf <- comf[which(!is.na(comf))]
comf <- gsub("Extremely comfortable","1",comf)
comf <- gsub("Moderately comfortable","2",comf)
comf <- gsub("Slightly comfortable","3",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","5",comf)
comf <- gsub("Moderately uncomfortable","5",comf)
comf <- gsub("Extremely uncomfortable","7",comf)
comf1 <- as.numeric(comf)
comf1
mean(comf1)

# class 2 comfort
x$Q9
comf <- x$Q9
comf <- comf[which(comf!="")]
comf <- comf[which(!is.na(comf))]
comf <- gsub("Extremely comfortable","1",comf)
comf <- gsub("Moderately comfortable","2",comf)
comf <- gsub("Slightly comfortable","3",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","5",comf)
comf <- gsub("Moderately uncomfortable","5",comf)
comf <- gsub("Extremely uncomfortable","7",comf)
comf2 <- as.numeric(comf)
comf2
mean(comf2)

par(mfrow=c(2,1), cex=0.8)
hist(comf1)
hist(comf2)

wilcox.test(comf1,comf2)
t.test(comf1,comf2)

```


### How useful the classes were (Q4 v Q10) and 

* the overall student satisfaction with the classes (Q5 v Q11).

I also tried to determine if there was any correlation between: 

* how comfortable the students were answering the questions and either how useful, or how satisfied, they were with the classes (for either Class 1 or Class 2).

Lastly, it would be good to see if there were any correlations between:

* How comfortable the students were answering questions with their preferred style of class (Q13) or future class (Q14)

* How useful the classes were with their preferred style of class (Q13) or future class (Q14)
the overall student satisfaction with the classes with their preferred style of class (Q13) or future class (Q14)

I am not so worried about breaking the students down into in-person, watched recording or watched livestream; it could be interesting but I don’t think the numbers are anywhere big enough to get any useful data out of it.
