---
title: "Stats analysis for Mat"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
theme: cosmo
---

Source code: https://github.com/markziemann/survey_stats_mat

## Intro

A survey based study into student preferences for a polling tool in revision lessons.

## Questions

Below are the survey questions given to students.

#### Q1. "For Revision Class 1 (on Tuesday 6th August), did you:"

1. face-to-face

2. recording

3. livestream

4. did not attend

#### Q2. "If you attended Revision Class 1, did you answer any questions aloud in front of the class?"

1. Yes, 1

2. Yes >1

3. No

#### Q3. "How comfortable did you feel to answer questions in Revision Class 1?"

1. Extremely comfortable

4. Neutral

7. Extremely comfortable

#### Q4. "How would you rate the usefulness of Revision Class 1 for understanding the topics covered?"

1. Extremely useful

2. Very useful

3. Moderately useful

4. Slightly useful 

5. Not useful at all

#### Q5. "How would you rate your overall satisfaction with Revision Class 1?"

1. Very Satisfied

2. Satisfied

3. Somewhat Satisfied

4. Neutral

5. Somewhat Dissatisfied

6. Dissatisfied

7. Very Dissatisfied

#### Q6. "Any comments about Revision Class 1 and answering questions aloud during the class?"

Qualitative answer in text box.

#### Q7. "For Revision Class 2 (Monday 26th August, using the Socrative App), did you:"

1. Face-to-face

2. Recording

3. Livestream

4. Did not attend

#### Q8. "If you attended Revision Class 2, did you use the Socrative App to answer any questions?"

1. Yes, 1

2. Yes >1

3. No

#### Q9. "How comfortable did you feel to answer questions in Revision Class 2 using the Socrative App?"

1. Extremely comfortable

4. Neutral

7. Extremely comfortable

#### Q10. "How would you rate the usefulness of Revision Class 2 for understanding the topics covered?"

1. Extremely useful

2. Very useful

3. Moderately useful

4. Slightly useful 

5. Not useful at all

#### Q11. "How would you rate your overall satisfaction with Revision Class 2?"

1. Very Satisfied

2. Satisfied

3. Somewhat Satisfied

4. Neutral

5. Somewhat Dissatisfied

6. Dissatisfied

7. Very Dissatisfied

#### Q12. "Any comments about Revision Class 2 and using the Socrative App?"

Qualitative answer in text box.

#### Q13. "Overall, did you prefer Revision Class 1 (traditional method of answering questions aloud during the class), or Revision class 2 (using the Socrative App to answer questions)?"

1. Class 1 with traditional method

2. Class 2 with Socrative

#### Q14. "For future revision classes, which method would you prefer to be used?"

1. Traditional method

2. Socrative method

## Load the data

```{r,read}
x <- read.csv("Revision Class Survey SLE346 T2 2019_September 12, 2019_11.26_for MZ fmt.csv")
head(x)
str(x)

```

## Matt's direction for statistical analysis

For the comparison, I am mainly interested in the responses comparing Class 1 (verbal answers) with Class 2 (Socrative app).

I am not so worried about breaking the students down into in-person, watched recording or watched livestream; it could be interesting but I don’t think the numbers are anywhere big enough to get any useful data out of it.

So in my original analyses I am mostly interested in the following questions:

### Was there a difference in participation between traditional and socrative classes?

The first approach to answer will be to use the three levels of participation and test with a Wilcox test and generate the confidence intervals with a t-test.

```{r , participation}
# participation for class 1
part <- x$Q2
part <- part[which(part!="")]
part <- gsub('Yes \\(more than one question\\)',"2",part)
part <- gsub("No","0",part)
part1 <- as.numeric(part)
part1

# participation for class 2
part <- x$Q8
part <- part[which(part!="")]
part <- gsub('Yes \\(but only a few of the questions\\)',"1",part)
part <- gsub('Yes \\(all or almost all of the questions\\)',"2",part)
part <- gsub("No","0",part)
part2 <- as.numeric(part)
part2

par(mfrow=c(2,1), cex=0.8)
hist(part1)
hist(part2)

wilcox.test(part1,part2)
t.test(part1,part2)
```

According to the t-test the participation was significantly higher in class 2.

An alternative approach would be to perform binary classify of students as non-participants or participants and then run a Fisher exact test.

```{r , fisher1}
part1
class1_nonparticipants = length(which(part1==0))
class1_participants = length(which(part1!=0))
class2_nonparticipants = length(which(part2==0))
class2_participants = length(which(part2!=0))
row1 <- c(class1_nonparticipants,class1_participants)
row2 <- c(class2_nonparticipants,class2_participants)
y <- rbind(row1,row2)
rownames(y) <- c("class1","class2")
colnames(y) <- c("non participation","participation")
y
fisher.test(y)

# participation rate class 1 (%)
p1 = y[1,2]/sum(y[1,])*100
p1

# participation rate class 2 (%)
p2 = y[2,2]/sum(y[2,]) *100
p2

# increase in participation (%)
p2/p1 * 100
```

Again the p-value is very small indicating a significantly higher participation rate in the Socrative class.

### Were students more comfortable to participate in answering questions in traditional or Socrative classes? 

I have inverted the values to make it a measure of comfort. 
That means bigger numbers are "good".
This can be used in Wilcox test or t-test on ranks. Scale: 1 (extremely uncomf) to 7 (extremely comf).


```{r, comfort}
# class 1 comfort
x$Q3
comf <- x$Q3
comf <- comf[which(comf!="")]
comf <- comf[which(!is.na(comf))]
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf <- gsub("Extremely uncomfortable","1",comf)
comf1 <- as.numeric(comf)
comf1
mean(comf1)

# class 2 comfort
x$Q9
comf <- x$Q9
comf <- comf[which(comf!="")]
comf <- comf[which(!is.na(comf))]
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf <- gsub("Extremely uncomfortable","1",comf)
comf2 <- as.numeric(comf)
comf2
mean(comf2)

par(mfrow=c(2,1), cex=0.8)
hist(comf1)
hist(comf2)

wilcox.test(comf1,comf2)
t.test(comf1,comf2)

```

This result indicates that participants were significantly more comfortable to participate with Socrative as compared to traditional/conventional method.

### Did students perceive traditional or Socrative classes to be more useful?

Same approach as above but the scale goes from 1 (not useful at all) to 5 (extremely useful).

```{r, useful}
# class 1 utility
x$Q4
us <- x$Q4
us <- us[which(us!="")]
us <- us[which(!is.na(us))]
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us <- gsub("Not at all useful","1",us)
us1 <- as.numeric(us)
us1
mean(us1)

# class 2 utility
x$Q10
us <- x$Q10
us <- us[which(us!="")]
us <- us[which(!is.na(us))]
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us <- gsub("Not at all useful","1",us)
us2 <- as.numeric(us)
us2
mean(us2)

par(mfrow=c(2,1), cex=0.8)
hist(us1, xlim = c(1,5))
hist(us2, xlim = c(1,5))

wilcox.test(us1,us2)
t.test(us1,us2)
```
Students ranked Socrative classes higher but there was no significant difference.

### Were students more satisfied with traditional or Socrative classes?

Satisaction was on a scale of 1 (extremely dissatisfied) to 7 (extremely dissatisfied). 

```{r, satisfaction}
# class 1 satisfaction
x$Q5
sat <- x$Q5
sat <- sat[which(sat!="")]
sat <- sat[which(!is.na(sat))]
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Unsatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat <- gsub("Satisfied","6",sat)
sat1 <- as.numeric(sat)
sat1
mean(sat1)

# class 2 satisfaction
x$Q11
sat <- x$Q11
sat <- sat[which(sat!="")]
sat <- sat[which(!is.na(sat))]
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Disatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat <- gsub("Satisfied","6",sat)
sat2 <- as.numeric(sat)
sat2
mean(sat2)

par(mfrow=c(2,1), cex=0.8)
hist(sat1,xlim=c(1,7))
hist(sat2,xlim=c(1,7))

wilcox.test(sat1,sat2)
t.test(sat1,sat2)

```

These results indicate average satisfaction was higher in Class 2 however it was not statistically significant.

### Does the level of comfort with answering questions correlate with perceived utility or satisfaction?

how comfortable the students were answering the questions and either how useful, or how satisfied, they were with the classes (for either Class 1 or Class 2).

Class 1 comfort

```{r}
# class 1: comfort = Q3, utility=Q4, satisfaction=Q5
x$Q3
comf <- x$Q3
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf1 <- gsub("Extremely uncomfortable","1",comf)
comf1

# class 1 utility
x$Q4
us <- x$Q4
us <- us[which(us!="")]
us <- us[which(!is.na(us))]
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us1 <- gsub("Not at all useful","1",us)
us1

# class 1 satisfaction
x$Q5
sat <- x$Q5
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Dissatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat1 <- gsub("Satisfied","6",sat)
sat1

# check with another method because worries about NA values
z <- cbind(comf1,us1,sat1)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z

cor.test(z[,1],z[,2])
cor.test(z[,1],z[,3])

```

This result shows that there is no significant correlation between comfort and either usefulness or satisfaction in class 1. Now I can do the same for class 2.

```{r}
# class 2: comfort = Q9, utility=Q10, satisfaction=Q11
# class 1: comfort = Q3, utility=Q4, satisfaction=Q5
x$Q9
comf <- x$Q9
comf <- gsub("Extremely comfortable","1",comf)
comf <- gsub("Moderately comfortable","2",comf)
comf <- gsub("Slightly comfortable","3",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","5",comf)
comf <- gsub("Moderately uncomfortable","6",comf)
comf2 <- gsub("Extremely uncomfortable","7",comf)
comf2

# class 1 utility
x$Q10
us <- x$Q10
us <- us[which(us!="")]
us <- us[which(!is.na(us))]
us <- gsub("Extremely useful","1",us)
us <- gsub("Very useful","2",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","4",us)
us2 <- gsub("Not at all useful","5",us)
us2

# class 1 satisfaction
x$Q11
sat <- x$Q11
sat <- gsub("Very Satisfied","1",sat)
sat <- gsub("Somewhat Satisfied","3",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","5",sat)
sat <- gsub("Very Unsatisfied","7",sat)
sat <- gsub("Dissatisfied","6",sat)
sat1 <- gsub("Satisfied","2",sat)
sat2

# check with another method because worries about NA values
z <- cbind(comf2,us2,sat2)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z

cor.test(z[,1],z[,2])
cor.test(z[,1],z[,3])
```
This result shows that there is no significant correlation between comfort and either usefulness or satisfaction in class 2 either.

### Is there a correlation between How comfortable the students were answering questions with their preferred style of class (Q13) or future class (Q14)

Not completely sure how to calculate this one.
One solution would be to make a ratio of comfort for the two class types and then correlate the ratio with preferred class type.
Responses to Q13 and Q14 were nearly identical so I will only analyse Q13 preferred class.

```{r}
# class 1 comfort
x$Q3
comf <- x$Q3
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf1 <- gsub("Extremely uncomfortable","1",comf)

# class 2 comfort
x$Q9
comf <- x$Q9
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf2 <- gsub("Extremely uncomfortable","1",comf)

x$Q13
pref <- x$Q13
pref <- gsub("Class 1 \\(traditional method\\)","1",pref)
pref <- gsub("Class 2 \\(using Socrative\\)","2",pref)
pref

z <- cbind(comf1,comf2,pref)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
# the ratio here is important because it is a negative scale
z$rat <- z$comf2 - z$comf1
z
cor.test(z$rat,z$pref)
```

This result suggests there is a weak association between class comfort level and preference but it is not significant.

### Is there a correlation between how useful the classes were and their preferred style of class (Q13) or future class (Q14)

```{r}
# class 1 usefulness
x$Q4
us <- x$Q4
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us1 <- gsub("Not at all useful","1",us)
us1

# class 2 usefulness
x$Q10
us <- x$Q10
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us2 <- gsub("Not at all useful","1",us)
us2

# preference
x$Q13
pref <- x$Q13
pref <- gsub("Class 1 \\(traditional method\\)","1",pref)
pref <- gsub("Class 2 \\(using Socrative\\)","2",pref)
pref

z <- cbind(us1,us2,pref)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
# note the direction of the ratio
z$rat <- z$us2 - z$us1
z
cor.test(z$rat,z$pref)
```

This result suggests there is a weak negative association between perceived usefullness and preference but it is not significant.

### Is there a correlation between student satisfaction with the classes with their preferred style of class (Q13) or future class (Q14)

```{r}
# class 1 satisfaction
x$Q5
sat <- x$Q5
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Dissatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat1 <- gsub("Satisfied","6",sat)
sat1

# class 2 satisfaction
x$Q11
sat <- x$Q11
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Dissatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat2 <- gsub("Satisfied","6",sat)
sat2

# preference
x$Q13
pref <- x$Q13
pref <- gsub("Class 1 \\(traditional method\\)","1",pref)
pref <- gsub("Class 2 \\(using Socrative\\)","2",pref)
pref

z <- cbind(sat1,sat2,pref)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
# note the direction of the ratio
z$rat <- z$sat2 - z$sat1
z
cor.test(z$rat,z$pref)

```

This result suggests there is a weak association between satisfaction and preference but it is not significant.

### Is there an association between differential participation level and preferred class type?

```{r}
# participation for class 1
part <- x$Q2
part <- gsub('Yes \\(more than one question\\)',"2",part)
part1 <- gsub("No","0",part)
part1
# participation for class 2
part <- x$Q8
part <- gsub('Yes \\(but only a few of the questions\\)',"1",part)
part <- gsub('Yes \\(all or almost all of the questions\\)',"2",part)
part2 <- gsub("No","0",part)
part2

# preference
x$Q13
pref <- x$Q13
pref <- gsub("Class 1 \\(traditional method\\)","1",pref)
pref <- gsub("Class 2 \\(using Socrative\\)","2",pref)
pref <- as.numeric(pref)
pref

z <- cbind(part1,part2,pref)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)

# note the direction of the ratio
z$rat <- z$part2 - z$part1
z
cor.test(z$rat,z$pref)
```

There was no clear association between participation level and the preferred class. 

### Is there an association between level of comfort and participation in Revision Class 1?

Class 1 - level of comfort (Q3)

Class 1 - participation (Q2) 

```{r}
# participation for class 1
part <- x$Q2
part <- gsub('Yes \\(more than one question\\)',"2",part)
part <- gsub("No","0",part)
part1 <- as.numeric(part)
part1


# class 1 comfort
x$Q3
comf <- x$Q3
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf <- gsub("Extremely uncomfortable","1",comf)
comf1 <- as.numeric(comf)
comf1

z <- cbind(comf1,part1)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
z
cor.test(z$comf1,z$part1)
```

There is no correlation, likely because there was too little participation.

### Is there an association between level of comfort and participation in Revision Class 2?

Class 2 - level of comfort (Q9)

Class 2 - participation (Q8) 

```{r}
# participation for class 2
part <- x$Q8
part <- gsub('Yes \\(but only a few of the questions\\)',"1",part)
part <- gsub('Yes \\(all or almost all of the questions\\)',"2",part)
part <- gsub("No","0",part)
part2 <- as.numeric(part)
part2

# class 2 comfort
x$Q9
comf <- x$Q9
comf <- gsub("Extremely comfortable","7",comf)
comf <- gsub("Moderately comfortable","6",comf)
comf <- gsub("Slightly comfortable","5",comf)
comf <- gsub("Neither comfortable nor uncomfortable","4",comf)
comf <- gsub("Slightly uncomfortable","3",comf)
comf <- gsub("Moderately uncomfortable","2",comf)
comf <- gsub("Extremely uncomfortable","1",comf)
comf2 <- as.numeric(comf)
comf2

z <- cbind(comf2,part2)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
z
cor.test(z$comf2,z$part2)
```

There is a strong correlation between comfort level and participation (p=0.002).

### Is there an association between usefulness and student satisfaction in Revision Class 1?

Class 1 - usefulness (Q4)

Class 1 - satisfaction (Q5) 

```{r}
# class 1 utility
x$Q4
us <- x$Q4
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us <- gsub("Not at all useful","1",us)
us1 <- as.numeric(us)
us1

# class 1 satisfaction
x$Q5
sat <- x$Q5
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Unsatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat <- gsub("Satisfied","6",sat)
sat1 <- as.numeric(sat)
sat1

z <- cbind(us1,sat1)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
z
cor.test(z$us1,z$sat1)
```

There was a positive association between perceived utility and satisfaction (p=0.025).

### Is there an association between usefulness and student satisfaction in Revision Class 1?

Class 2 - usefulness (Q10)

Class 2 - satisfaction (Q11) 

```{r}
# class 2 utility
x$Q10
us <- x$Q10
us <- gsub("Extremely useful","5",us)
us <- gsub("Very useful","4",us)
us <- gsub("Moderately useful","3",us)
us <- gsub("Slightly useful","2",us)
us <- gsub("Not at all useful","1",us)
us2 <- as.numeric(us)
us2

# class 2 satisfaction
x$Q11
sat <- x$Q11
sat <- gsub("Very Satisfied","7",sat)
sat <- gsub("Somewhat Satisfied","5",sat)
sat <- gsub("Neutral","4",sat)
sat <- gsub("Somewhat Dissatisfied","3",sat)
sat <- gsub("Very Unsatisfied","1",sat)
sat <- gsub("Dissatisfied","2",sat)
sat <- gsub("Satisfied","6",sat)
sat2 <- as.numeric(sat)
sat2

z <- cbind(us2,sat2)
z <- apply(z,2,as.numeric)
z <- z[!is.na(rowSums(z)),]
z <- as.data.frame(z)
z
cor.test(z$us2,z$sat2)
```

There was a strong association between perceived utility and satisfaction (p=2.0e-8).

## Conclusions

There was a massive difference in student participation between class types, with the Socrative app resulting in a much higher participation rate.
Students were more comfortable using the Socrative app as compared to traditional/conventional methods.
Traditional and socrative classes were viewed as useful with only a small difference between them. 
When students passively attend class they may have a false sense of security because they lack chances to benchmark own performance with formative assessment.
Similarly there was no significant difference in satisfaction between class types.
There was no significant correlation between comfort with answering questions and perceived utility or satisfaction in either class.
Students that participated more in class 2 as compared to class 1 tended to prefer Socrative over traditional methods (p=0.09).
There was no correlation between differential utility and preference.
There was no correlation between differential satisfaction and preference.
While the simple comparisons gave a clear result, the correlation analyses likely require a larger sample size.
Correlation analysis between level of comfort and participation shows no assocation in class 1 but strong association in class 2.
Perceived utility was correlated with student satisfaction in both class 1 and 2.

## Session information

```{r,session}
sessionInfo()
```

